---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rawKS

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/rawKS)](https://CRAN.R-project.org/package=rawKS)
[![Travis build status](https://travis-ci.org/JiaxiangBU/rawKS.svg?branch=master)](https://travis-ci.org/JiaxiangBU/rawKS)
[![DOI](https://zenodo.org/badge/194376668.svg)](https://zenodo.org/badge/latestdoi/194376668)
<!-- badges: end -->

The goal of rawKS is to easily extract the raw KS statistics to plot and report.
The Python version [pyks](https://github.com/JiaxiangBU/pyks) is hosted from GitHub.

## Installation

You can install the released version of rawKS from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rawKS")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaxiangBU/rawKS")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r,child="vignettes/intro.Rmd"}
```

## Citations

```{r include=FALSE}
citations <- add2pkg::add_zenodo_citation("README.Rmd")
```

```{r echo=FALSE, results='asis'}
cat(citations$Cite)
```

```{r echo=FALSE, results='asis'}
cat(paste0("```BibTex\n",citations$BibTex,"\n```"))
```

```{r echo=FALSE, results='asis'}
cat(citations$Comments)
```


`r add2pkg::add_disclaimer("Jiaxiang Li")`
